The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-05-22 article.tex
EOD

From an alignment, we run a Bayesian analysis and 
create a posterior distribution of trees and parameters
using the \verb;babette; (\cite{babette}) package
that sets the input parameters similar to BEAUti 2 and then runs BEAST2. 
For our site model, we assume a Jukes-Cantor 
nucleotide substitution model, as used in the simulation of the alignment.
For our clock model, we assume a strict clock with the same fixed rate as 
used in the simulation of the alignment. 
The tree prior assumed in inference is the BD model, 
because studying the effect of this assumption is the goal of this study. 
We assume an MRCA prior with a tight normal distribution
around the crown age, by choosing the crown age as mean, and a standard deviation 
of $0.5 \cdot 10^{-3}$ time units,
resulting in 95\% of the crown ages inferred have the same resolution (of $10^{-3}$ time 
units) as the alignment. 
We ran the MCMC chain to generate 1111 states,
of which we remove the first 10\% (also called the 'burn-in'). 
Of the remaining
1000 MCMC states, the effective sample size (ESS) of the posterior \textbf{[NOTE: there
is a parameter estimate called 'posterior'. I choose to pick that one, and I assume
it is the wiser choice over 'prior' and parameter estimates. Must discuss]} must at least be 200
for a strong enough inference (\cite{beastbook}). An ESS can be increased by increasing
the number of samples or decreasing the autocorrelation between samples. 
If the ESS is less than 200, we decrease autocorrelation by doubling 
the MCMC sampling interval of that simulation, until the ESS exceeds 200.

>>>>

From an alignment, we run a Bayesian analysis and 
create a posterior distribution of trees and parameters
using the \verb;babette; (\cite{babette}) package
that sets the input parameters similar to BEAUti 2 and then runs BEAST2. 
For our site and clock model, we assume a Jukes-Cantor 
nucleotide substitution model and strict clock model, 
as those are also used for simulating that alignment.
We set the BD model as a tree prior, 
as gauging the effect of this incorrect assumption is the goal of this study. 
We assume an MRCA prior with a tight normal distribution
around the crown age, by choosing the crown age as mean, and a standard deviation 
of $0.5 \cdot 10^{-3}$ time units,
resulting in 95\% of the crown ages inferred have the same resolution (of $10^{-3}$ time 
units) as the alignment. 
We ran the MCMC chain to generate 1111 states,
of which we remove the first 10\% (also called the 'burn-in'). 
Of the remaining
1000 MCMC states, the effective sample size (ESS) of the posterior \textbf{[NOTE: there
is a parameter estimate called 'posterior'. I choose to pick that one, and I assume
it is the wiser choice over 'prior' and parameter estimates. Must discuss]} must at least be 200
for a strong enough inference (\cite{beastbook}). An ESS can be increased by increasing
the number of samples or decreasing the autocorrelation between samples. 
If the ESS is less than 200, we decrease autocorrelation by doubling 
the MCMC sampling interval of that simulation, until the ESS exceeds 200.
